Exploring the composition of lithic assemblages in Mesolithic south-eastern Norway

### 2021-08-01 analysis/paper/paper.Rmd
Added OSF link

The exploratory approach taken here means that a wide range of combinations and transformations of variables has been explored to identify patterning in the data. While only parts of this process can sensibly be reported upon, the data and employed R programming script is freely available as a research compendium at [URL placeholder], following @marwick2018b.

>>>>

The exploratory approach taken here means that a wide range of combinations and transformations of variables has been explored to identify patterning in the data. While only parts of this process can sensibly be reported upon, the data and employed R programming script is freely available as a research compendium at https://osf.io/ehjfc/, following @marwick2018b.
